# Creating Vectors

the c() function can be used to create vectors of objects

```{r}

x <- c(0.5, 0.6) ##numeric
x <- c(TRUE, FALSE) ## logical
x <- c(T, F) ## logical
x <- c("a", "b", "c", "D") ## chaacter
x <- 9:29 ## integer
x <- c(1+0i, 2+4i) ## complex
```

**Using the vector() function**

```{r}

x <- vector("numeric", length = 20)
```

### Mixing Objects

What about the following?

```{r}
y <- c(1.7, "a") ## chactery
y <- c(TRUE, 2) ## numeric
y <- c("a", TRUE) ## charcter

```

### 

### Explicit Coercion

```{r}
x <- 0:6
as.numeric(x)
as.logical(x)
as.character(x)
```

Nonsensical coercion results in NAS

```{r}

x <- c ("c", "b", "a")
as.logical(x)

as.numeric(x)

as.complex(x)
```

## List

Lists are a special type of vector that can contain elements of different classes. Lists are a very
important data type in R and you should get to know them well. Lists, in combination with the
various \"apply\" functions discussed later, make for a powerful combination.

Lists can be explicitly created using the **list() function**, which takes an arbitrary number of
arguments.

```{r}
x <- list(1, "a", TRUE, 1 + 4i)
```
